Implications of afforestation policies for global markets

### 2023-05-31 paper.Rmd
Update paper.Rmd

The global gains that can be realized from afforestion, however, are uncertain, with broad estimates of cumulative sequestration ranging from 42 gigatonnes to 700 gigatonnes by the end of the century [@veldman2019]  [@bastin201]  [@Humpenöder2014]  [@sathaye2006]. In addition, the amount of land conversion that would be required also varies greatly, with estimates ranging from 0.3 billion hectares to 2.8 billion hectares [@veldman2019]  [@bastin201]  [@Humpenöder2014].  In many cases, these results suggest massive losses in pasture and cropland. At the same time, forests are continually threatened by issues such as rising incomes and food prices and population growth that put pressure on policymakers to allow greater conversion of forestland into farmland. Previous research though has suggested that substantive gains in the carbon sink (+23.8PgCo2e/yr) can be made without sacrificing agricultural land [@griscom2017]. Still, the manner in which these various and oftentimes competing concerns are addressed will have significant impacts on the global community.

@@

South America and Sub-Saharan Africa are two regions that show much potential for afforestation. It is estimated that these two regions hold at least 50% of the potential global gain while regions such as Northern Africa and the Middle East show little promise as growth rates are quite low [@doelman2020]. Thus, it is promising that the African Forest Landscape Restoration Initiative (AFR100) aims to afforest 100 million hectares by 2030 with roughly 70% of the committments coming from Sub-Saharan nations [@auda2023]. While many of these nations may be well-suited in biophysical terms for afforestation, there is concern about how long-lasting any investment may be due to proximate zones of political instability. Other nations that have a big potential for gains from afforestation face different challenges. India has a great potential to increase its carbon sequestration through afforestation, but due to its masssive population and food security worries, its NDC does not entertain the idea of agricultural land being repurposed and instead primarily considers targeting wastelands that may not be well suited for afforestation [@amjath2019].

These are not the only concerns that need to be considered by policymakers planning afforestation activities, as for example, oelman2020].

.

>>>>

The global gains that can be realized from afforestion, however, are uncertain, with broad estimates of cumulative sequestration ranging from 42 gigatonnes to 700 gigatonnes by the end of the century [@veldman2019]  [@bastin201]  [@Humpenöder2014]  [@sathaye2006]  [@doelman2020]. In addition, the amount of land conversion that would be required also varies greatly, with estimates ranging from 0.3 billion hectares to 2.8 billion hectares [@veldman2019]  [@bastin201]  [@Humpenöder2014]  [@doelman2020].  In many cases, these results suggest massive losses in pasture and cropland. This puts into question the feasibility of attaining these results, as forests are continually threatened by issues such as rising incomes and food prices and population growth that put pressure on policymakers to allow greater conversion of forestland into farmland. Previous research though has suggested that substantive gains in the carbon sink (+23.8PgCo2e/yr) can be made without sacrificing agricultural land [@griscom2017]. Still, the manner in which these various and oftentimes competing concerns are addressed will have significant impacts on the global community.

@@

South America and Sub-Saharan Africa are two regions that show much potential for afforestation. It is estimated that these two regions hold at least 50% of the potential global gain while regions such as Northern Africa and the Middle East show little promise as forest growth rates are quite low [@doelman2020]. Thus, it is promising that the African Forest Landscape Restoration Initiative (AFR100) aims to afforest 100 million hectares by 2030 with roughly 70% of the committments coming from Sub-Saharan nations [@auda2023]. While many of these nations may be well-suited in biophysical terms for afforestation, there is concern about how long-lasting any investment may be due to proximate zones of political instability. There are other nations that have a big potential for gains from afforestation, but they also face challenges. India, for example, has a great potential to increase its carbon sequestration through afforestation, but due to its masssive population and food security worries, its NDC does not entertain the idea of agricultural land being repurposed and instead primarily considers targeting wastelands that may not be well suited for afforestation [@amjath2019].
